Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 raspi_journal.tex
expanded results multicore
Finished SRLNC for now..

%=================================================================
\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
\synctex=1
\usepackage{fixme}

@@

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
$^{4}$ \quad SFB 912 -- HAEC}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{This research has been financed by the CROSSFIRE MITN Marie
Curie project (317126) from the European Comission FP7 framework,
the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B)
, the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted
by the Danish Council for Independent Research (Det Frie Forskningsr\r{a}d),
and by the German Research Foundation (DFG) within the Collaborative Research Center SFB 912 – HAEC.}

>>>>

%=================================================================
\documentclass[electronics,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
\synctex=1
\usepackage{fixme}
\usepackage{caption}
\usepackage{subcaption}

@@

\usepackage[]{algorithm2e}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwurf ApS. Aalborg, Denmark; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems. Aalborg, Denmark; \{nh, cws, del\}@es.aau.dk\\
$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks. Dresden, Germany; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
$^{4}$ \quad SFB 912 -- Collaborative Research Center HAEC. Dresden, Germany}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{This research has been partially financed by the
Marie Curie Initial Training Network (ITN) CROSSFIRE project
(Grant No. EU - FP7 - CROSSFIRE - 317126) from the European Comission FP7
framework, the Green Mobile Cloud project (Grant No. DFF - 0602 - 01372B),
the TuneSCode project (Grant No. DFF - 1335 - 00125) both granted by the
Danish Council for Independent Research (Det Frie Forskningsr\r{a}d), and
by the German Research Foundation (DFG) within the Collaborative Research
Center SFB 912 – HAEC.}

### 2016-06-01 schemes.tex
Finished SRLNC for now..

For this method, we first calculate the amount of coding coefficients
that we will use to combine. To do it so, a random number $\mathbb{N}$
of the original packets is used to produce a coded packet. For our case,
$\mathbb{N}$ is binomially distributed with parameters $g$ for the number
of trials and $d$ for its success probability, e.g. $\mathbb{N} \sim
Binomial(g,d)$. However, when sampling from this distribution, the case
$\mathbb{N} = 0$ occurs with a non-zero probability. In order to handle
this special case, our implementation considers
$\mathbb{K} = \max(1,\mathbb{N})$ as the final amount of packets to be
mixed together. In this way, we always ensure that at least one packet is
encoded.

The only caveat is that the case of $\mathbb{K} = 1$ occurs slightly
more often than in the original distribution, but for the
considered density range in this method it is depreciable
\textbf{Same reference here}. Then, once the distribution number of packets
to mix as been defined, we create a subset $\mathcal{C}$ of size $k$

a coded packetas is shown in
\eqref{eq:sparse_coded_packet2}, that implementation
proved faster for low densities \textbf{reference?}. It is best expressed as:
%
\begin{align} \label{eq:sparse_coded_packet2}
    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{im} \otimes P_{m} ,\
    %L \subseteq \{1,\dots,g\}: |L|=k ,\
    \forall i \in [1,g] ,\
    v_{ij} > 0
\end{align}
where
$m = \text{choice}(\{1,\dots,g\}, \text{size}=k, \text{replace}=\text{False})$.
\fxnote{Can this be represented smarter?}

It is often desired to express the coding density as $d=\frac{k}{g}$. We call
this notation $k-sparse$ where $k$ is the average number of packets combined to
produce a coded packet.

>>>>

For this method, we first obtain the amount of packets
that we will combine to create a coded packet. To do it so, a random
number $\mathbb{N}$ of the original packets is used to produce a
coded packet. For our case, $\mathbb{N}$ is binomially distributed
with parameters $g$ for the number of trials and $d$ for its success
probability, e.g. $\mathbb{N} \sim Binomial(g,d)$. However,
when sampling from this distribution, the case
$\mathbb{N} = 0$ occurs with a non-zero probability. In order to handle
this special case, our implementation considers
$\mathbb{K} = \max(1,\mathbb{N})$ as the final amount of packets to be
mixed together. In this way, we always ensure that at least one packet is
encoded.

The only caveat is that the case of $\mathbb{K} = 1$ occurs slightly
more often than $\mathbb{N} = 1$ in the original distribution, but for
the considered density range in this method, this is not a significant
modification \textbf{Same reference here}. Then, once the distribution for the
number of packets to mix has been defined, we sample a value $n$ from
$\mathbb{N}$ and compute $k = \max(1,n)$. Later, we create a create a
set $\mathcal{K}$ with cardinality $k$, e.g. $|\mathcal{K}| = k$,
where the elements in $\mathcal{K}$ are the indexes of the packets that are
going to be considered for making a coded packet. To compute the indexes
of the set $\mathcal{K}$, we do the following algorithm in pseudo-code: \\
\ \\
\begin{algorithm}[H]
 \label{alg:k_set}
 \KwData{$k$: Size of $\mathcal{K}$. $g$: Generation Size}
 \KwResult{$\mathcal{K}$: The set of non-repeated indexes}
 $\mathcal{K}$ = \{ \}\;
 \While{$|\mathcal{K}| \neq k$ }{
  $i$ = Sample from $\mathbb{U}(1,g)$\;
  \If{$i \notin \mathcal{K}$}{
   Insert $i$ in $\mathcal{K}$\;
   }
 }
 \caption{Computation of the set of indexes for packet combination in SRLNC.}
\end{algorithm}
\ \\
Where in Algorithm~\ref{alg:k_set}, the notation $\mathbb{U}(1,g)$ stands
for a uniform discrete random variable with limits $1$ and $g$. The
pseudo-code in Algorithm~\ref{alg:k_set} indicates that the set $\mathbb{K}$
is filled with non-repeated elements taken uniformly at random from
$[1,\ldots,g]$. Finally, once the set of indexes has been defined, a coded
packet using \ac{SRLNC} can be written as shown in
\eqref{eq:sparse_coded_packet2}:
%
\begin{align} \label{eq:sparse_coded_packet2}
    C_i  &= \bigoplus_{m \in \mathcal{K}} v_{im} \otimes P_{m},\ v_{im} \neq 0,\ \forall i \in [1,\ldots)
    %L \subseteq \{1,\dots,g\}: |L|=k ,\
\end{align}

% It is often desired to express the coding density as $d=\frac{k}{g}$. We call
% this notation $k-sparse$ where $k$ is the average number of packets combined to
% produce a coded packet.
